\documentclass[12pt]{article}
\input{etc/resume-style.sty}

\begin{document}

\input{etc/resume-header.tex}

% ==============================================================================

\bigskip

\hspace{6.75em} Ecologist, evolutionary biologist \& botanist

\

2023--     \hspace{3.75em} \textbf{Research \& Publishing Intern} \\
           \hspace{6.75em} C4 EcoSolutions \\
\

2023       \hspace{4.25em} \textbf{MSc} in Biological Sciences \\
           \hspace{6.75em} University of Cape Town \\
\

2015--2022 \hspace{1.5em} \textbf{Teaching Assistant \& Tutor} (various) \\
           \hspace{6.75em} Departments of Biological Sciences, \\
                            \hspace{13em} Mathematics \& Applied Mathematics, \\
                            \hspace{13em} Statistical Sciences \\
           \hspace{6.75em} University of  Cape Town \\
           \ \\
           \hspace{6.75em} \textbf{Research Assistant} (various) \\
           \hspace{6.75em} Department of Biological Sciences \\
           \hspace{6.75em} University of Cape Town \\
\

2017       \hspace{4.25em} \textbf{BSc Hons} in Biological Sciences \\
           \hspace{6.75em} \textit{With distinction} \\
           \hspace{6.75em} University of Cape Town \\
\

2016       \hspace{4.25em} \textbf{BSc} in Ecology \& Evolution, Applied Biology \\
           \hspace{6.75em} \textit{With distinction in both majors \& the degree as a whole} \\
           \hspace{6.75em} University of Cape Town \\
\

\hrule % -----------------------------------------------------------------------

\bigskip

\textbf{Languages}     \hfill                  English, Afrikaans, \texttt{R}

\textbf{Tools    }     \hfill                            \texttt{R} Markdown,
                                        {\fontfamily{lmr}\selectfont \LaTeX},
                               \texttt{bash}, \texttt{git}, GitHub, MS Office

\textbf{Skills  }      \hfill Statistical modelling, data manipulation, visualisation, GIS (in \texttt{R}), \\
                       \hfill phylogeny inference \& comparative methods, functional programming

\

\hrule % -----------------------------------------------------------------------

\bigskip

\textbf{Recent publications}

\vskip5pt

\textbf{Van Mazijk}, Cramer, \& Verboom. 2021.  Environmental heterogeneity explains contrasting plant species richness between the South African Cape \& southwestern Australia. \textit{J.~Biogeog.} 48. \href{https://doi.org/10.1111/jbi.14118}{10.1111/jbi.14118}.

Elliott, \textbf{van Mazijk}, Barrett, Bruhl, Joly, Muthaphuli, Wilson, \& Muasya. 2021. Global dispersal \& diversification of the genus \textit{Schoenus} (Cyperaceae) from the Western Australian biodiversity hotspot. \textit{J.~Syst.~Evol.} 59(4). \href{https://doi.org/10.1111/jse.1274}{10.1111/jse.12742}.

\end{document}
