\documentclass[10pt]{article}
\input{etc/style.sty}

\begin{document}

\input{etc/header.tex}

\bigskip

\input{etc/education.tex}

\subsection*{Publications} % ---------------------------------------------------

\input{etc/publications.tex}

\hrulefill

\begin{multicols}{2}

\textbf{Funding, awards \& conferences}\\ % ------------------------------------

Student sponsorship to attend MEDECOS {\small
  (NRF\footnote{National Research Foundation
  (South Africa)})}                                \hfill {\small       2022} \\
Presented at IBS\footnote{International
  Biogeography Society} ECBC\footnote{Early Career
  Biogeographers Conference}                       \hfill {\small       2021} \\
Candidate at iDiv\footnote{German Centre for
  Integrative Biodiversity Research,
  Halle-Jena-Leipzig} Joint Recruitment Symposium  \hfill {\small       2020} \\
Best Systematics MSc Presentation at                                          \\
\hspace{2em} SAAB\footnote{South African
  Association of Botanists}-AMA\footnote{African
  Mycological Association}-SASSB\footnote{Southern
  African Society for Systematic Biology} (tie)    \hfill {\small       2019} \\
Innovation Masters Schol.          {\small  (NRF)} \hfill {\small       2019} \\
MSc Student Bursary                {\small (SAAB)} \hfill {\small 2018--2019} \\
                                                      % (inaugural recipient)
Once-Off Award                     {\small  (UCT)} \hfill {\small       2018} \\
Travel grant for SAAB-AMA-SASSB    {\small  (UCT)} \hfill {\small       2018} \\
Dorothy Cameron Schol.             {\small  (UCT)} \hfill {\small       2018} \\
Masters Research Schol.            {\small  (UCT)} \hfill {\small       2018} \\
Innovation Honours Schol.          {\small  (NRF)} \hfill {\small       2017} \\
Honours Schol.                     {\small (SAAB)} \hfill {\small       2017} \\
Science Faculty Schol.             {\small  (UCT)} \hfill {\small 2015--2016}

\columnbreak

\textbf{Teaching assistance} % -------------------------------------------------
  ~~{\small \textmd{\textit{All for undergrad. unless stated}}}\\

Angiosperm diversity                         \hfill {\small 2018--2019, 2022} \\
Data wrangling \& manipulation in \textit{R}                                  \\
\hspace{2em} (\textit{Organised \& lead
  workshop})                                 \hfill {\small             2019} \\
Principles of ecology \& evolution           \hfill {\small       2019--2020} \\
Scientific study design \& data analysis in
  \textit{R}                                 \hfill {\small       2017--2020} \\
                           % NOTE: finished tutoring for STA2007* in Aug 2020
Teaching Biodiversity for High School Life                                    \\
\hspace{2em} Science Teachers {\small
  (SDU\footnote{UCT Schools Development Unit}
  short course)}                             \hfill {\small             2019} \\
Stat. modelling in \textit{R} {\small
  (SEEC\footnote{UCT Centre for Statistics in
  Ecology, the Environment \&
  Conservation}-ACCESS\footnote{NRF Applied
  Centre for Climate \& Earth Systems} short
  course)}                                   \hfill {\small             2018} \\
Introductory statistics in \textit{R}        \hfill {\small       2016--2018}

\textbf{Professional affiliations}\\ % -----------------------------------------

SASSB council member, student representative           \hfill {\small 2019--} \\
                                                         % term ends end-2021
SASSB student member                                   \hfill {\small 2018--} \\
SAAB student member                                    \hfill {\small 2017--}

\end{multicols}

\textbf{Research assistance}\\ % -----------------------------------------------

\textit{Schoenus} spp.~(Cyperaceae: Schoeneae)
  collections \& growth for
  Dr T.L.~Elliott \&
  Prof A.M.~Muasya {\small (UCT)}                                  \hfill {\small 2018} \\
\textit{Mimetes} spp.~\&
  \textit{Leucospermum} spp.~(Proteaceae) population
  monitoring for Dr J.A.~Slingsby
  {\small (SAEON\footnote{South African Environmental
  Observation Network}, SEEC)}                           \hfill {\small 2017} \\
Legume symbiotic rhizobia collections \& culturing for
  Dr M.~Dludlu {\small (University of Swaziland)}        \hfill {\small 2015}

\begin{multicols}{2}

\textbf{References} % ----------------------------------------------------------
  ~~{\small \textmd{\textit{All from the Dept. Biological Sciences (UCT)}}}

Prof G.~Anthony Verboom
      \hfill     \href{mailto:tony.verboom@uct.ac.za}{tony.verboom@uct.ac.za} \\
Prof Michael D.~Cramer
      \hfill \href{mailto:michael.cramer@uct.ac.za}{michael.cramer@uct.ac.za} \\
Prof A.~Muthama Muasya
      \hfill \href{mailto:muthama.muasya@uct.ac.za}{muthama.muasya@uct.ac.za} \\
Prof Adam G.~West
      \hfill           \href{mailto:adam.west@uct.ac.za}{adam.west@uct.ac.za}

\columnbreak

\textbf{Skills \& misc.} % -----------------------------------------------------

%\begin{center}
%  \textit{Wine drinker, amateur cartoonist}
%\end{center}

Skills         \hfill \textit{Strong public speaker, visual design, teaching} \\
Languages      \hfill \textit{                   English, Afrikaans, R, bash} \\
Tools          \hfill \textit{      R Markdown, LaTeX, git, GitHub, MS Offce} \\
Methods        \hfill \textit{Stat.~modelling, data manipulation, GIS (in R)}

\end{multicols}

\end{document}
