\documentclass[10pt]{article}
\input{style.sty}

\begin{document}

% Header
{\Large
\textbf{Ruan van Mazijk}, \textit{Curriculum vitae}
  \hfill ruanvmazijk@gmail.com, (+27) 72 516 7570
}

\hrulefill

\subsection*{Education} % ------------------------------------------------------

\begin{hangparas}{2em}{1}

\textbf{MSc candidate} in Biological Sciences
  (UCT\footnote{University of Cape Town})
  \hfill 2018--- \break
\textit{Genome-size effects on plant hydraulic ecophysiology, habitat \&
  phenology in Cape schoenoid sedges} \break
Principle supervisor: A/Prof A.M. Muasya. Co-supervisors: A/Prof G.A. Verboom
 \& A/Prof A.G. West

\textbf{BSc Hons} in Biological Sciences
  ~~(UCT)---Graduated with distinction
  \hfill 2017 \break
\textit{Relating vascular plant species richness \& environmental heterogeneity
  spatially in the GCFR \& SWAFR} \break
Supervisors: Prof M.D. Cramer \& A/Prof G.A. Verboom

\textbf{BSc} in Ecology \& Evolution, Applied Biology
  ~~(UCT)---Graduated with distinction in both majors \& the degree
  \hfill 2016 \break

\hfill

\end{hangparas}

\subsection*{Publications} % ---------------------------------------------------

\begin{hangparas}{2em}{1}

Elliott, T.L., Laidler, G., Muasya, A.M., Muthaphuli, N. \& \textbf{van Mazijk, 
R.} (In press). Foregrounding sedges: bringing the neglected Cape Schoenoid 
sedges to the forefront of genomic research. \textit{Veld \& Flora.} (Popular 
article)

Cramer, M.D., Wootton, L.M., \textbf{van Mazijk, R.} \& Verboom, G.A. (In 
review). Improved spatial soil data confirms dependence of vegetation 
distribution on edaphic properties in the Cape biodiversity hotspot. \textit{
Divers. Distrib.}

\textbf{Van Mazijk, R.}, Cramer, M.D. \& Verboom, G.A. (In prep.). The role of
environmental heterogeneity in determining plant species richness in the GCFR \&
SWAFR. \textit{J. Biogeogr.}

\textbf{Van Mazijk, R.}, Smyth, L.K., Weideman, E.A. \& West, A.G. (2018).
Isotopic tracing of stormwater in the urban Liesbeek River. \textit{Water SA}
44(4):674--679. DOI: 10.4314/wsa.v44i4.16.

% Shaik, Z., **van Mazijk**, R., Bergh, N.G., Verboom, G.A. and Cron, G. (In 
% prep.). Contingent evolution of sexual systems and life histories in 
% _Helichrysum_ (Asteraceae: Gnaphaleae).

\hfill

\end{hangparas}

\begin{multicols}{2}

\subsection*{Funding \& awards} % ----------------------------------------------

% "Justified" table based on <https://tex.stackexchange.com/questions/204112/how-to-fully-justify-tabular-columns>
%\begin{tabularx}{\textwidth}{@{}@{\extracolsep{\fill}}lr@{}} %r
%Best MSc Presentation at
%  SAAB\footnote{South African Association of Botanists}-AMA\footnote{African
%  Mycological Association}-SASSB\footnote{Southern African Society for 
%  Systematic Biology} IVXV\footnote{45\textsuperscript{th} Annual SAAB, AMA \& 
%  SASSB Joint Congress} (tie) {\footnotesize (SASSB)} &
%  %&
%  2019 \\
%Innovation Masters Scholarship {\footnotesize (DST\footnote{Department of 
%  Science \& Technology (South Africa)}-NRF\footnote{National Research 
%  Foundation (South Africa)})} &
%  %R90,000 &
%  2019 \\
%MSc Student Bursary (inaugural recipient) {\footnotesize (SAAB)} &
%  %R20,000 &
%  2018--2019 \\
%Once-Off Award {\footnotesize (UCT)} &
%  %R5,520 &
%  2018 \\
%Travel grant for SAAB-AMA-SASSB IVXV {\footnotesize (UCT)} &
%  %R3,819 &
%  2018 \\
%Dorothy Cameron Scholarship {\footnotesize (UCT)} &
%  %R20,000 &
%  2018 \\
%Masters Research Scholarship {\footnotesize (UCT)} &
%  %R30,000 &
%  2018 \\
%Innovation Honours Scholarship {\footnotesize (DST-NRF)} &
%  %R60,000 &
%  2017 \\
%Honours Scholarship {\footnotesize (SAAB)} & 
%  %R10,000 &
%  2017 \\
%Science Faculty Scholarship {\footnotesize (UCT)} &
%  %2$\times$R15,000 &
%  2015--2016 \\
%&
%  %\textit{Approx. total R270,000\footnote{ca. \$18,800 or €16,800}} &
%  \\
%\end{tabularx}

Best Systematics MSc Presentation at \\
\hspace{2em} SAAB\footnote{South African Association of Botanists}-AMA
  \footnote{African
  Mycological Association}-SASSB\footnote{Southern African Society for 
  Systematic Biology} IVXV\footnote{45\textsuperscript{th} Annual SAAB, AMA \& 
  SASSB Joint Congress} (tie)
  \hfill 2019 \\
Innovation Masters Scholarship {\footnotesize (DST\footnote{Department of 
  Science \& Technology (South Africa)}-NRF\footnote{National Research 
  Foundation (South Africa)})}
  \hfill 2019 \\
MSc Student Bursary (inaugural recipient) {\footnotesize (SAAB)}
  \hfill 2018--2019 \\
Once-Off Award {\footnotesize (UCT)}
  \hfill 2018 \\
Travel grant for SAAB-AMA-SASSB IVXV {\footnotesize (UCT)}
  \hfill 2018 \\
Dorothy Cameron Scholarship {\footnotesize (UCT)}
  \hfill 2018 \\
Masters Research Scholarship {\footnotesize (UCT)}
  \hfill 2018 \\
Innovation Honours Scholarship {\footnotesize (DST-NRF)}
  \hfill 2017 \\
Honours Scholarship {\footnotesize (SAAB)}
  \hfill 2017 \\
Science Faculty Scholarship {\footnotesize (UCT)}
  \hfill 2015--2016

\begin{center}
\textit{Total ca. US\$18,800 or €16,800}
\end{center}


\columnbreak

\subsection*{% -----------------------------------------------------------------
  Teaching assistance
  ~~{\footnotesize \textmd{\textit{
    All undergrad. courses unless stated
  }}}
}

Principles of ecology \& evolution
  \hfill 2019--- \\
Angiosperm diversity
  \hfill 2018--- \\
Scientific study design \& data analysis in \textit{R}
  \hfill 2017--- \\
Teaching Biodiversity for High School Life Science \\
  \hspace{2em} Teachers {\footnotesize
  (SDU\footnote{Schools Development Unit (UCT)} short course)}
  \hfill 2019 \\
Statistical modelling in \textit{R} {\footnotesize (SEEC\footnote{Centre for 
  Statistics in Ecology, the Environment \& Conservation (UCT)}-ACCESS\footnote{
  DST-NRF Applied Centre for Climate \& Earth Systems} short course)}
  \hfill 2018 \\
Introductory statistics in \textit{R}
  \hfill 2016--2018 \\
Mathematics for biology, earth \& environmental sci.
  \hfill 2015

%\columnbreak

\subsection*{Professional affiliations} % --------------------------------------

SASSB council member, student representative \hfill 2019--- \\
% term ends end-2021
SAAB student member \hfill 2017---

\end{multicols}

\hrulefill
\subsection*{% -----------------------------------------------------------------
  References 
  ~~{\footnotesize \textmd{\textit{
    All from the Dept. Biological Sciences (UCT)
  }}}
}

\begin{tabular}{lrr}
A/Prof G.A. Verboom & tony.verboom@uct.ac.za   & (+27) 21 650 3398 \\
Prof M.D. Cramer    & michael.cramer@uct.ac.za & (+27) 21 650 2444 \\
A/Prof A.M. Muasya  & muthama.muasya@uct.ac.za & (+27) 21 650 3725 \\
A/Prof A.G. West    & adam.west@uct.ac.za      & (+27) 21 650 3628
\end{tabular}

\end{document}
