Ismail, Duker, \textbf{van Mazijk}, Mills \& Potts.
The importance of ground-truthing for thicket restoration    \hfill In prep. \\
\hspace{2em} site-selection: distinguishing degraded solid thicket from natural thicket mosaics. \textit{Ecol.~Rest.}

Ismail, \textbf{van Mazijk}, Duker \& Mills.
\textit{Portulacaria~afra} canopies support diverse understory plant growth-forms
                                                              \hfill In prep. \\
\hspace{2em} in southern African xeric succulent thicket. \textit{J.~Arid~Env.}

Mills \& \textbf{van Mazijk}.
Non-parametric permutation testing to identify significant constraint promotion                                                     \hfill In prep. \\
\hspace{2em} within biological scatterplots.
  \textit{Ecol.~Evol.}

Mills, \textbf{van Mazijk}, Allen \& Strydom.
Soil geochemistry \& constraint of tree seedlings immediately after
                                                              \hfill In rev. \\
\hspace{2em} germination on \textit{Macrotermes} termite
  mounds in the Kruger National Park, South Africa.
  \textit{Oikos}

\textbf{Van Mazijk}, West, Verboom, Elliott, Bureš \& Muasya.
Genome size variation in Cape schoenoid sedges                \hfill In rev. \\
\hspace{2em} (Cyperaceae: Schoeneae) \& its ecophysiological consequences.
  \textit{Am.~J.~Bot.}

Mills, Duker, Lechmere-Oertel, \textbf{van Mazijk} \& Potts.
Science is the fuel required for lifting ecosystem             \hfill In press \\
\hspace{2em} restoration into the orbit of hundreds of millions of hectares.
  \textit{Front.~Cons.~Sci.}

\textbf{Van Mazijk}, Cramer \& Verboom.
Environmental heterogeneity explains contrasting plant species richness
                                                                  \hfill 2021 \\
\hspace{2em}
  between the South African Cape \& southwestern Australia.
  \textit{J.~Biogeog.}
  48. \href{https://doi.org/10.1111/jbi.14118}{10.1111/jbi.14118}.

Elliott, \textbf{van Mazijk}, Barrett, Bruhl,
Joly, Muthaphuli, Wilson \& Muasya.
Global dispersal \& diversification of                            \hfill 2021 \\
\hspace{2em}
  the genus \textit{Schoenus} (Cyperaceae)
  from the Western Australian biodiversity hotspot.                           \\
\hspace{2em}
  \textit{J.~Syst.~Evol.}
  59(4).
  \href{https://doi.org/10.1111/jse.1274}{10.1111/jse.12742}.

Elliott, Laidler, Muasya, Muthaphuli \& \textbf{van Mazijk}.
Solving the sedge mystery.
\textit{Veld \& Flora}~105(3):20--25.                             \hfill 2019

Cramer, Wootton, \textbf{van Mazijk} \& Verboom.
New regionally-modelled soil layers improve prediction of         \hfill 2019 \\
\hspace{2em}
  vegetation type relative to that based on global soil models.
  \textit{Div.~Distrib.}
  25(11).                                                        
  \href{https://doi.org/10.1111/ddi.12973}{10.1111/ddi.12973}.

\textbf{Van Mazijk}, Smyth, Weideman \& West.
Isotopic tracing of stormwater in the urban Liesbeek River.
\textit{Water~SA}                                                 \hfill 2018 \\
\hspace{2em}
  44(4).
  \href{https://doi.org/10.4314/wsa.v44i4.16}{10.4314/wsa.v44i4.16}.
